Real-Time Certified Probabilistic Pedestrian Forecasting

### 2017-02-15 pedestrian_forecasting_iros_2017.tex
Resize images

\begin{figure}
	\centering
	\begin{subfigure}[b]{.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/FirstPage/gates_1_2_t=55.png}
		\caption{$t=1.83s$}
	\end{subfigure}
		\begin{subfigure}[b]{.45\linewidth}
			\includegraphics[width=\linewidth]{./figures/FirstPage/gates_1_2_t=145.png}
			\caption{$t=4.83$}
		\end{subfigure}

	\begin{subfigure}[b]{.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/FirstPage/gates_1_2_t=235.png}
		\caption{$t=7.83s$}
	\end{subfigure}
	\begin{subfigure}[b]{.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/FirstPage/gates_1_2_t=345.png}
		\caption{$t=11.5s$}
	\end{subfigure}
	\caption{The performance of the presented algorithm captures the most probable routes that a pedestrian chooses. In this example which was captured at thirty frames per second, the presented algorithm took 0.0158s per frame in a Python implementation.  In this figure, the dot is the start point of the test trajectory, the diamond is the position at time $t$, and the X is the end of the trajectory.}
	\label{fig:gates-1-2}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{Our Algorithm}}   
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/ours_death_1_2_t=70.png}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/ours_death_1_2_t=250.png}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/ours_death_1_2_t=370.png}
	\end{minipage}

	\vspace{0.1cm}
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{Kitani et al.}} 
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/kit_death_1_2_t=70.png}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/kit_death_1_2_t=250.png}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/kit_death_1_2_t=370.png}
	\end{minipage}

	\vspace{0.1cm}
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{Random Walk} }
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/rand_death_1_2_t=70.png}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/rand_death_1_2_t=250.png}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/rand_death_1_2_t=370.png}
	\end{minipage}

@@

\begin{figure}
	\centering
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{Our Algorithm}   }
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/ours_1_2_t=50.png}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/ours_1_2_t=130.png}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/ours_1_2_t=370.png}
	\end{minipage}

	\vspace{0.1cm}
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{Kitani et al.}  }
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/kit_1_2_t=50.png}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/kit_1_2_t=130.png}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/kit_1_2_t=370.png}
	\end{minipage}

	\vspace{0.1cm}
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{Random Walk} }  
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/rand_1_2_t=50.png}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/rand_1_2_t=130.png}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/rand_1_2_t=370.png}
	\end{minipage}

>>>>

\begin{figure}
	\centering
	\begin{subfigure}[b]{.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/FirstPage/gates_1_2_t=55.jpg}
		\caption{$t=1.83s$}
	\end{subfigure}
		\begin{subfigure}[b]{.45\linewidth}
			\includegraphics[width=\linewidth]{./figures/FirstPage/gates_1_2_t=145.jpg}
			\caption{$t=4.83$}
		\end{subfigure}

	\begin{subfigure}[b]{.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/FirstPage/gates_1_2_t=235.jpg}
		\caption{$t=7.83s$}
	\end{subfigure}
	\begin{subfigure}[b]{.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/FirstPage/gates_1_2_t=345.jpg}
		\caption{$t=11.5s$}
	\end{subfigure}
	\caption{The performance of the presented algorithm captures the most probable routes that a pedestrian chooses. In this example which was captured at thirty frames per second, the presented algorithm took 0.0158s per frame in a Python implementation.  In this figure, the dot is the start point of the test trajectory, the diamond is the position at time $t$, and the X is the end of the trajectory.}
	\label{fig:gates-1-2}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{Our Algorithm}}   
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/ours_death_1_2_t=70.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/ours_death_1_2_t=250.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/ours_death_1_2_t=370.jpg}
	\end{minipage}

	\vspace{0.1cm}
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{Kitani et al.}} 
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/kit_death_1_2_t=70.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/kit_death_1_2_t=250.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/kit_death_1_2_t=370.jpg}
	\end{minipage}

	\vspace{0.1cm}
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{Random Walk} }
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/rand_death_1_2_t=70.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/rand_death_1_2_t=250.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/rand_death_1_2_t=370.jpg}
	\end{minipage}

@@

\begin{figure}
	\centering
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{Our Algorithm}   }
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/ours_1_2_t=50.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/ours_1_2_t=130.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/ours_1_2_t=370.jpg}
	\end{minipage}

	\vspace{0.1cm}
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{Kitani et al.}  }
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/kit_1_2_t=50.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/kit_1_2_t=130.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/kit_1_2_t=370.jpg}
	\end{minipage}

	\vspace{0.1cm}
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{Random Walk} }  
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/rand_1_2_t=50.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/rand_1_2_t=130.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/rand_1_2_t=370.jpg}
	\end{minipage}
